---
title: GLOSSARY
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: iow_logo_horizontal_rgb.png
    theme: readable
runtime: shiny
---
<script>
$('.navbar-logo').wrap('<a href="http://internetofwater.org">');
</script>

<style type="text/css">

.chart-title {  /* chart_title  */
   font-size: 20px;
   font-family: "Quicksand",Sans-serif;
   color: #022949;
   font-weight: bold

}


.navbar-inverse .nav-collapse .nav > li > a {
 font-size:40px;
}
</style>



```{r global, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(shiny)
library(DT)
library(urltools)
#library(rdflib)
library(shinyWidgets)
#library(igraph)
library(SPARQL)
library(shinyLP)

downloadButtonRmd <- function (outputId, label = "Download", class = NULL, ...)  {
     tags$a(id = outputId, class = paste("btn btn-default shiny-download-link", 
        class), href = "", target = "_blank", download = NA, 
        icon("download"), label, ...)
 }

## big table
#g<-rdf_parse("glossary.ttl",format="turtle")
endpoint<-"http://35.238.222.96:7200/repositories/Glossary_core"
q<-'PREFIX skos: <http://www.w3.org/2004/02/skos/core#>
PREFIX : <http://purl.org/iow/Glossary/>

select ?uri ?Term ?Vocabulary ?voclink ?Organization ?Definition ?Theme  WHERE { 
	?uri a skos:Concept .
    ?uri skos:prefLabel ?Term .
    ?uri skos:definition ?Definition .
    ?uri skos:inScheme ?voc .
    ?voc skos:note ?voclink .
    ?voc skos:prefLabel ?Vocabulary .
    ?voc rdfs:isDefinedBy ?Org .
    ?Org skos:prefLabel ?Organization .
    ?Th skos:member ?uri .
    ?Th skos:prefLabel ?Theme
}'

data<-SPARQL(endpoint,q,format="csv")$results
data[] <- lapply(data, as.character)

Terms<-distinct(data[c("uri","Term","Vocabulary")])%>%arrange(Term)
Terms$Term<-paste0(Terms$Term," (",Terms$Vocabulary,")")
data$Vocabulary <- paste0('<a href=', data$voclink,' target="_blank" rel="noopener"','>',data$Vocabulary,'</a>')
data$Term <- paste0(data$Term,'<a href=', data$uri,' target="_blank" rel="noopener"','> ',as.character(icon("share", lib = "glyphicon")),'</a>')
data<-data[c("uri","Term","Definition","Vocabulary","voclink","Organization","Theme")]



```




Main Term Browser
=====================================  

Column {data-width=650}
-----------------------------------------------------------------------

### Main Table of Terms
<h5>Filter by Theme and/or Organization. Click rows to view synonyms and related terms on the right.</h5>

```{r}

ch<-unique(data[order(data$Theme),]$Theme)
ch<-c(ch,"Other")
data$Theme[which(is.na(data$Theme))]<-"Other"
d <- reactive({
  data%<>%filter(Theme %in% input$filter & Organization %in% input$filter2  )%>%arrange(Term)%>%distinct(uri,.keep_all=T)
})


fluidRow(column(1,pickerInput(
   inputId = "filter",
   #label = "Theme(s)",
    choices = ch,
   selected= ch,
   multiple=TRUE, width=300, options = list(
      `actions-box` = TRUE, `selected-text-format`='static',`title`="Select Theme(s)")
),offset=1),
column(1,pickerInput(
   inputId = "filter2",
 #  label = "Organizations(s)",
    choices = unique(data[order(data$Organization),]$Organization),
   selected=unique(data[order(data$Organization),]$Organization),
   multiple=TRUE, width=300, options = list(
      `actions-box` = TRUE, `selected-text-format`='static',`title`="Select Organization(s)")
),offset=3))




#d2 <- reactive({d()[c("Concept","Definition")]})

output$table = DT::renderDataTable({
  DT::datatable(d(), options = list(columnDefs = list(list(targets = c(0,4,5,6), visible = FALSE),list(targets=c(0,3,4,5,6),searchable=FALSE)),
    dom='Bti', buttons = list(list(extend = 'csv', filename= 'main_table')),bPaginate=FALSE,scrollY='55vh',searchHighlight = TRUE), rownames=FALSE, escape=FALSE, selection="single", extensions = c('Buttons','FixedHeader'), filter="top"
  )
})

DT::dataTableOutput('table')

#, scrollY = '65vh')


```



Column {data-width=350}
-----------------------------------------------------------------------

### Synonyms of selected term


```{r}
 s = reactive({as.character(d()[input$table_rows_selected,"uri"])})
 synparse<-reactive({paste0('PREFIX skos: <http://www.w3.org/2004/02/skos/core#>
PREFIX : <http://purl.org/iow/Glossary/>
select ?uri where{
    <',s(), '> skos:exactMatch ?uri
}')})
 syn_uris<-reactive({SPARQL(endpoint,synparse(),format="csv")$result$uri})

 syn_d<-reactive({data<-data%>%filter(uri %in% syn_uris())})


 output$syntable = DT::renderDataTable({
   DT::datatable(syn_d(), extensions = c('Buttons','Responsive'),options = list(columnDefs = list(list(targets = c(0,4,5,6), visible = FALSE),list(targets=c(0,3,4,5,6),searchable=FALSE)),
     dom='Bt', buttons = list(list(extend = 'csv', filename= paste0('synonyms','_',substr(s(),nchar(s())-10,nchar(s()))))),"pageLength" = 5000,scrollY='70vh'), rownames=FALSE, escape=FALSE, selection="single"
   )
 })

DT::dataTableOutput('syntable')


```

Help Identify Synonyms
=====================================  



Column {data-width=650}
-----------------------------------------------------------------------

### Browse Terms

<h5>Step 1: Select term to for which to identify synonyms</h5>

```{r}
fluidRow(column(1,pickerInput(
   inputId = "search",
  # label = "Search Terms (with source vocabulary)", 
   width=600,
    choices = Terms$Term,
  selected=NULL,
options = list(  size = 10, `live-search` = TRUE)
)

,offset=1))

selected_uri<-reactive({as.character(Terms$uri[which(Terms$Term == input$search)])})
```

<h5>Step 2. Click all rows corresponding to terms you believe are synonymous with the term selected in Step 1. The glossary has provided the 50 terms with the most commonality in the word content of definitions ("score")  to the selected term.</h5>
```{r}
sel_parse<-reactive({paste0('PREFIX :<http://www.ontotext.com/graphdb/similarity/>
PREFIX inst:<http://www.ontotext.com/graphdb/similarity/instance/>
PREFIX pubo: <http://ontology.ontotext.com/publishing#>
PREFIX skos: <http://www.w3.org/2004/02/skos/core#>

SELECT ?Term ?Definition ?Vocabulary ?score {
    ?search a inst:definition_text_similarity ;
        :searchDocumentID <',selected_uri(), '>;
        :searchParameters "-numsearchresults 50";
        :documentResult ?result .
    ?result :value ?documentID ;
            :score ?score.
    ?documentID skos:prefLabel ?Term .
    ?documentID skos:definition ?Definition .
    ?documentID skos:inScheme ?voc .
    ?voc skos:prefLabel ?Vocabulary .
}')})
sel_uris<-reactive({SPARQL("http://35.238.222.96:7200/repositories/Synonym_search",sel_parse(),format="csv")$result%>%mutate(score=round(score,2))})

 output$seltable = DT::renderDataTable({
   DT::datatable(sel_uris(),options = list(
     dom='ti',"pageLength" = 5000,scrollY='55vh',buttons = list(list(extend = 'csv', filename= paste0('synonyms_submit')))), rownames=FALSE, escape=FALSE, selection="multiple"
   )
 })

DT::dataTableOutput('seltable')

```

Under construction. There will be three columns. In column one you select the term you want to identify synonyms for. In column two there is a list of the 100 closest terms to the selected term according to the similarity of the text in the definitions ([see here for description of method](http://text2vec.org/similarity.html)) The user can select any number of these terms. In column three is the table of the selected terms. Upon review, the the user fills out their name and contact information, and the results are sent to a google sheet where synonym proposals can be reviewed by IoW and/or WaDE staff.


Column {data-width=350}
-----------------------------------------------------------------------
### Review proposed synoynms

<h5>Step 3. Review and submit synonym suggestions</h5>


```{r}

#print(reactive({input$seltable_rows_selected}))
sel_syn = reactive({sel_uris()[c(1,input$seltable_rows_selected),]})

 output$selsyn = DT::renderDataTable({
   DT::datatable(sel_syn()[c("Term","Definition","Vocabulary")], extensions = c('Buttons','Responsive'),options = list(
     dom='Bt', buttons = list(list(extend = 'csv', filename= paste0('synonyms_submit'))),"pageLength" = 5000,scrollY='55vh'), rownames=FALSE, escape=FALSE, selection="single"
   )
 })

DT::dataTableOutput('selsyn')
#
# iframe(width = "560", height = "315",
# url_link = s())

```



Submit Your Vocabulary
=====================================  

Column 
-----------------------------------------------------------------------

### Submit your vocabulary

We are in the process of collecting vocabularies in use by public water resources and quality agencies, NGOs, and private-sector organizations across the country. If you did not see your organization's vocabulary/ies represented in our Main Term Browser tab, please consider contributing a vocabulary to our Glossary! 


[Click here to contribute](https://ee.kobotoolbox.org/i/::BQ2kodoV)

